Sparse Function-space Representation \\ of Neural Networks

### 2023-05-16 paper/main.tex
Colours

@@

% The methods
\definecolor{darkgray176}{RGB}{176,176,176} % darkgray176
\definecolor{color-our}{RGB}{0,191,191} %darkturquoise0191191
\definecolor{color-mlp}{RGB}{191,0,191} % darkviolet1910191
\definecolor{color-ddpg}{RGB}{191,191,0} % goldenrod1911910
\definecolor{green01270}{RGB}{0,127,0} % green01270
\definecolor{lightgray204}{RGB}{204,204,204} % lightgray204

@@

\cref{fig:rl} shows training curves for using \our as the dynamic model (\lab{color-our}), along with a Laplace-GGN~\cite{ADD} with GLM predictions (\lab{black})\todo{Arno cannot see these colour, someone help}, an ensemble of neural networks (\lab{black}), and a basic MLP without uncertainty (\lab{color-mlp}). To ensure a fair comparison, we maintain the same MLP architecture/training scheme across all these methods and incorporate them into the same model-based RL algorithm (see \cref{app:rl}). We also compare our results with Deep Deterministic Policy Gradient (DDPG, \cite{lillicrapContinuousControlDeep2016}), a model-free RL algorithm (\lab{color-ddpg}).
%
The training curves clearly show that \our's uncertainty estimates help exploration as it converges in fewer episodes, demonstrating higher sample efficiency. As expected, the MLP strategy (without uncertainty) was not able to successfuly explore the environment.

>>>>

\paragraph{Implementation} We implement all methods in PyTorch~\ref{todo}

\paragraph{Toy examples} \cref{fig:teaser} and \cref{fig:banana}

@@

% The methods
\definecolor{darkgray176}{RGB}{176,176,176} % darkgray176
\definecolor{color-our}{RGB}{0,191,191} %darkturquoise0191191
\definecolor{color-mlp}{RGB}{191,0,191} % darkviolet1910191
\definecolor{color-ddpg}{RGB}{191,191,0} % goldenrod1911910
\definecolor{color-ensemble}{RGB}{0,127,0} % green01270
\definecolor{lightgray204}{RGB}{204,204,204} % lightgray204

@@

\cref{fig:rl} shows training curves for using \our as the dynamic model (\lab{color-our}), along with a Laplace-GGN~\cite{ADD} with GLM predictions (\lab{red}), an ensemble of neural networks (\lab{color-ensemble}), and a basic MLP without uncertainty (\lab{color-mlp}). To ensure a fair comparison, we maintain the same MLP architecture/training scheme across all these methods and incorporate them into the same model-based RL algorithm (see \cref{app:rl}). We also compare our results with Deep Deterministic Policy Gradient (DDPG, \cite{lillicrapContinuousControlDeep2016}), a model-free RL algorithm (\lab{color-ddpg}).
%
The training curves clearly show that \our's uncertainty estimates help exploration as it converges in fewer episodes, demonstrating higher sample efficiency. As expected, the MLP strategy (without uncertainty) was not able to successfuly explore the environment.
